Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd
Add test code for #14

```{r, echo=FALSE, eval=FALSE}
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "ref.bib")
wordcountaddin::word_count("article.Rmd")
```

>>>>

```{r, echo=FALSE, eval=FALSE}
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "ref.bib")
wordcountaddin::word_count("article.Rmd")
knitr::purl("article.Rmd")
file.copy("article.R", "code/article-methods-1.R")
```
